%!TEX root=../partitions.tex

\url{https://www.youtube.com/watch?v=DF38ml9QeV8}
\url{https://tabs.ultimate-guitar.com/tab/pink-floyd/comfortably-numb-tabs-79177}
[B-] ~ [A] ~ [G] ~ [E-] ~ [B-]
Hello, hello, hello
Is there anybody in there?
Just nod if you can hear me.
Is there anyone at home?


Come on, come on down,
I hear you're feeling down.
Well I can ease your pain,
Get you on your feet again.

Relax, relax, relax
I need some information first.
Just the basic facts.
Can you show me where it hurts?

[D] ~ [A] 
There is no pain, you are receding.
A distant ship's smoke on the horizon.
[C] ~ [G] 
You are only coming through in waves.
Your lips move, but I can't hear what you're saying.

When I was a child, I had a fever.
My hands felt just like two balloons.

Now I've got that feeling once again.
I can't explain, you would not understand.
This is not how I am.
[A] ~ [C] ~ [G] ~ [D]
I have become comfortably numb.

[guitar solo]

I have become comfortably numb.

OK, OK, OK
Just a little pin prick.
There'll be no more, aaaaaaaaaaaahhhhhhhhh,
But you may feel a little sick.

Can you stand up, stand up, stand up.
I do believe it's working good.
That'll keep you going for the show.
Come on, it's time to go.

There is no pain, you are receding.
A distant ship's smoke on the horizon.
You are only coming through in waves.
Your lips move, but I can't hear what you're saying.

When I was a child, I caught a fleeting glimpse
Out of the corner of my eye.
I turned to look, but it was gone.
I cannot put my finger on it now.
The child has grown, the dream is gone.
I have become comfortably numb. 